\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
first attempt of description of GTE and GENIE3

>>>>

GTE is a method which characterizes a relationship between neurons by an estimation of the generalized transfer entropy (\cite{stetter2012model}). The goal of this method tries to see if the next time step value is better from the previous values of this time series or from time series of other neurons.

GENIE3 is a tree-based method which sees the network inference problem as $p$, the number of variables, independent supervised learning problems (todo cite: Irrthum?Van Anh?Pierre?). Formally, each sub-problem consists in the prediction of one variable, the target, from the remaining $p-1$ variables. This method uses random forests to estimate the target variable and variable importances can be derived to estimate the adjacency matrix $A$ (see (todo cite) for a more detailed description of the inference method).
